---
title: "Trends in ecology and conservation over eight decades"
author:
- "Sean C. Anderson^1^"
- "Paul R. Elsen^2^"
- "Brent B. Hughes^3^"
- "Rebecca K. Tonietto^4^"
- "Add Your Name Here in Alphabetical Order^X^"
date: |
  ^1^Pacific Biological Station, Fisheries and Oceans Canada
     Nanaimo, BC, V6T 6N7, Canada; sean.anderson@dfo-mpo.gc.ca\
  ^2^Here\
  ^3^Department of Biology, Sonoma State University, Rohnert Park, CA 94928, USA\
  ^4^Department of Biology, University of Michigan-Flint, Flint, MI 48502, USA\
  ^X^Add Your Address Here
output:
  bookdown::pdf_document2:
    number_sections: no
    toc: no
    template: "article.tex"
bibliography: "refs.bib"
csl: "nature.csl"
link-citations: yes
linkcolor: "blue"
urlcolor: "blue"
abstract: >
  The abstract will go here.
---

\clearpage

```{r, echo = FALSE, message = FALSE}
library(knitr)
library(here)
opts_chunk$set(echo = FALSE, message = FALSE, warnings = FALSE)
```

<!--

The field of ecology has come a long way since the work of Linnaeus (REF),
Humboldt (REF), Wallace (REF) amongst many others in the 18th and 19th
centuries and has developed alongside the field of conservation, marked by
events such as the founding of the nature conservancy and influential books such
as Aldo Leopold's A Sand County Almanac and Rachel Carlson's Silent Spring.

The field of ecology developed rapidly in the twentieth century

The fields of ecology and conservation have developed rapidly since the work of
ecology and conservation have developed substantial..
-->

The field of ecology has experienced rapid growth since the discipline specific
journal, *Ecology*, was first published over a century ago [@reiners2017;
@kim2018]. Today, with hundreds of ecology journals representing a multitude of
subdisciplines, the field of ecology spans in scope from general to applied to
theoretical and has become increasingly intertwined with the fields of natural
history and conservation. In light of such growth and diversification,
accomplishing a broad overview of the field can be challenging.

The discipline of culturomics --- the quantitative analysis of large bodies of
text or corpa --- offers a rich framework with which to track the evolution of
a field through time [@michel2011; @ladle2016]. Specifically, word use in the
published literature can serve as a proxy for tracking realized, versus
perceived, importance. This approach has been applied to subsets of the
ecological literature, notably a century of titles and abstracts in the journal
*Ecology* [@kim2018], automated content analysis of titles and abstracts in top
ecology journals based on impact factor [@mccallen2019], and more specific
research questions restricted to certain regions or taxa [e.g., @beale2018].

Here, we build on previous analyses [e.g., @carmel2013; @reiners2017; @kim2018;
@mccallen2019] by providing the first full-text analysis of ecology and
conservation journals over eight decades encompassing 52 journals, 131,533
articles, and over half a billion words. We base our analysis on the JSTOR
full-text corpus of "n-grams" from 1930 to 2010 for all journals that regularly
publish ecological or conservation papers and are not regionally or
taxonomically exclusive (see Methods). An n-gram is a sequence of terms
separated by a space. For example, "biogeography" is a 1-gram and "body size" is
a 2-gram. We standardize n-gram frequency by total words per year and analyze
trends over time for a selection of n-grams. We derive our n-gram selection
through both algorithmic and hand-curated approaches: (1) drawing on the most
frequent and rapidly growing/declining n-grams in various decades and (2)
developing logical groupings of terms that fall under key ecology and
conservation themes (see Methods).

<!--
Might shorten some part of this down to a sentence and insert above ** PLEASE NOTE the text below is directly pulled from a different paper, but wondered if we may want to do the same ** .
[The corpus cannot be read by a human. If
you tried to read only English-language entries from the year 2000 alone, at
the reasonable pace of 200 words/min, without interruptions for food or sleep,
it would take 80 years. The sequence of letters is 1000 times longer than the
human genome: If you wrote it out in a straight line, it would reach to the
Moon and back 10 times over (8).]
-->

# Results

## Broad trends in popularity

A mission driven discipline: [@meine2006]

(Fig. \@ref(fig:decades)) (biggest then and now; biggest climbers (and biggest losers in Supp.)

We used a fill-in-the-blank strategy to algorithmically examine the dominant
2-grams associated with levels of scale in ecology (Fig. \@ref(fig:blanks)). We
found that *Species richness* and *plant species* have been the dominant
adjective and noun uses of the term species, respectively (Fig.
\@ref(fig:blanks)ab). The term *native* came from behind around 2000 to become
the third most common term proceeding *species* as of 2010 (Fig.
\@ref(fig:blanks)b). As an adjective, the term *population* has been primarily
associated with *size*, *growth*, *dynamics*, and *density*, with *population
growth* following approximately exponential growth itself (Fig.
\@ref(fig:blanks)d). Conversely, *natural* *population* was the dominant
noun-form of *population*, but was surpassed by *human population* as of 2010
(Fig. \@ref(fig:blanks)e). Ecologists have written about *community structure*,
and *community composition* more than any other adjective-form of *community*
and about *plant communities*, within our corpus, over three times(?) more than
any other form of community (Fig. \@ref(fig:blanks)gh). Ecologists first used
the term *ecosystem* as a noun long before using it as an adjective starting
around 1990 (Fig. \@ref(fig:blanks)jk). As a noun, *ecosystem* has been most
commonly associated with *forest*, *terrestrial*, and *marine*, with the latter
seeing a sharp uptick since 2000 (Fig. \@ref(fig:blanks)k). As an adjective,
*ecosystem service* and *ecosystem function* are by far the dominant 2-grams
(Fig. \@ref(fig:blanks)j).

Using the same approach, we examined adjectives associated with conservation,
diversity, experiment, and analysis (Fig. \@ref(fig:blanks)). *Biodiversity
conservation* did not appear until 1990(?) in our corpus but is now used over
twice as often as the next most common nature term, *nature conservation* (Fig.
\@ref(fig:blanks)c). *Genetic diversity* has skyrocketed since the early 1990s
to become the dominant adjective associated with diversity (Fig.
\@ref(fig:blanks)f). *Field* and *laboratory experiment* peaked around 1990 and
have been declining since (Fig. \@ref(fig:blanks)i). *Statistical*, the first
adjective associated with *analysis* that made the top eight terms, continued to
see growth as of 2010 (Fig. \@ref(fig:blanks)l); however, *data analysis*, which
didn't appear until 1950, surpassed statistical analysis around 2000 (Fig.
\@ref(fig:blanks)l). *Meta-analysis*, which first appeared in 1988(?) in our
corpus, has seen rapid growth to become the most common adjective associated
with analysis as of 2010 (Fig. \@ref(fig:blanks)l).

## Community ecology

Fig. \@ref(fig:ecology)

## Statistics and data analysis

Ecology has increasingly become a data- and model-centric discipline in recent
decades (Fig. \@ref(fig:decades)). *Regression*, an overarching term
encompassing many statistical approaches, saw continued and rapid growth in use
since the 1950s, approaching *correlation* by 2005 (Fig. \@ref(fig:methods)a).
References to *ANOVA* and *t-tests* both peaked around 2000, while mentions of
generalized linear models (*GLMs*) steadily increased in frequency surpassing
*t-tests* around 2007(?) (Fig. \@ref(fig:methods)a). In terms of how such models
were fit, *least-squares*, formerly the dominant paradigm, was rapidly surpassed
by *Bayesian*, *maximum likelihood*, and *information theoretic* terms around
2000; as of 2010, the term *Bayesian* was used over twice as often as *maximum
likelihood* (Fig. \@ref(fig:methods)b). The Markov chain Monte Carlo sampling
method (*MCMC*), which combined with modern computing power has been responsible
for the boom in applied Bayesian data analysis [@gelman2014b] first appears in
the corpus in 1994 [@thompson1994], 24 years after [@hastings1970] described the
concept. Such statistical approaches and paradigms have been associated with
endless debates about the role of hypothesis testing in ecology (REFs).
Regarding hypothesis testing, use of the phrase *null hypothesis* peaked in the
1980s and the phrase *significant difference* peaked around 1990 and has
declined since (Fig. \@ref(fig:methods)c). The associated terms *p-value* and
*confidence interval* appeared in approximately equal frequency as of 2010 (Fig.
\@ref(fig:methods)c), although both are often referred to by abbreviations
missed in our corpus (e.g. 'p =' or 'CI'). *Power analysis* remains a rarely
used term despite numerous pleas of its importance [@nakagawa2007; @smith2011d].
The increased frequency of so many data- and model-centric terms, along with the
advent of online publishing, has coincided with the meteoric rise of
*supplementary material* n-grams since around 2000 --- the 2-gram itself had the
second most rapid increase across all 2-grams from 2000--2010 (Fig.
\@ref(fig:decades)f) --- and a decline in *unpublished data* (Fig.
\@ref(fig:methods)d).

## Genetics
The focus on genetics in ecology and conversation related research has skyrocketed in the past several decades. This can be seen in the massive increase in the term *genetic diversity* (Figure 2f and 4e). Interestingly, phylogenetics has remained the most common referenced genetic term over the years, at a rapidly increasing rate since the 1990s (Fig 4e). With the advent of next-generation sequencing, we also see a fast increase in sequencing based approaches to studying genetic diveristy, particularly the rise in reference to *single nucleotide polymorphisms*  (Figure 4f). Interestingly, the term *epigenetics* has been in use since the 1950s (See Supplementary figure), before we had methods for studying epigenetics in the modern sense (Bird A (May 2007). "Perceptions of epigenetics". Nature. 447 (7143): 396–98). This is likely due to the fact that beginning the the 1940s, the term *epigenetics* was used to refer to the differentiation of cells during embryonic development (Waddington, C. H. (1942). "The epigenotype". Endeavour. 1: 18–20.). The term also has been used in developmental psychology (Gottlieb, G. (1991). "Epigenetic systems view of human development". Developmental Psychology. 27 (1): 33–34. doi:10.1037/0012-1649.27.1.33). 

## Conservation and applied ecology

*Conservation* and themes related to applied ecology represented some of the
fastest growing themes in modern ecology (Fig. \@ref(fig:decades)e).
Conservation as a field originated alongside the formation of the Society for
Conservation Biology in 1985 [@meine2006], prior to which the roughly synonymous
term *preservation* was used as frequently in ecological literature (Fig.
\@ref(fig:cons)a). *Biodiversity*, a core concept of conservation, replaced the
terminology *biological diversity* that had been in use since the 1960s.
Alongside *conservation*, *biodiversity* is one of the most rapidly growing
terms we analyzed in the corpus (Fig. 1e). Given the prominent focus on
biodiversity conservation in the field of ecology, ecologists have increasingly
studied the major threats to biodiversity loss: *habitat loss*, *invasive
species*, *pollution*, *overpopulation*, *overexploitation*, and *climate
change* (Fig. \@ref(fig:cons)b). Despite *overexploitation* being considered the
most prevalent threat of species extinctions worldwide [@maxwell2016], the
concept has received the least attention from ecologists both historically and
currently (Fig. \@ref(fig:cons)b). Up until the early 1990s, *pollution* was the
leading concept in the context of threats to biodiversity --- its use in the
ecological literature having peaked in the mid 1970s (Fig. \@ref(fig:cons)b).
Interestingly, frequencies of the concept *ozone*, typically associated with
studies of pollution, showed similar responses as *pollution*, but with a lag of
approximately 15 years (Fig. \@ref(fig:cons)c). *Pollution* was then surpassed
by *climate change* and subsequently by *invasive species*, two threats that now
vastly outweigh all other threats in terms of their frequency of usage (Fig.
\@ref(fig:cons)b) and two of the top three fastest growing terms in all of
ecology (Fig. 1f).

A multitude of concepts originated alongside the proliferation of studies of
climate change, habitat loss, and overexploitation (Fig. \@ref(fig:cons)c-e).
With such relatively recent concept formations, most of these concepts are
experiencing continued growth. For example, concepts related to climate change,
such as *ocean acidification*, *range shifts*, and *climate extremes* have shown
sharp upticks since the mid 2000s (Fig. \@ref(fig:cons)c). Other concepts have
shown more complex patterns. For example, *sea-level rise* showed a large spike
in usage in the mid 1990s, a dramatic downturn in usage by 2000, and then
another sharp increase thereafter (Fig. \@ref(fig:cons)c). *Fragmentation* rose
sharply following the common usage of *habitat loss* around 1990, but its use
has been in decline since about 2000 (Fig. \@ref(fig:cons)d). In terms of modes
of overexploitation, which include both methods of species exploitation and
resource extraction, *fishing* is currently the leading concept, followed by
*hunting* and *logging* (Fig. \@ref(fig:cons)e). Historically, *hunting* and
*fishing* have exchanged positions of dominance in the ecological literature
roughly every decade, showing predator-prey-like dynamics in their frequency
distributions over time (Fig. \@ref(fig:cons)e). Modes of exploitation of
non-animal resources, such as *logging*, *harvesting*, and *mining* have
consistently been discussed less in the ecological literature compared to modes
of animal exploitation (Fig. \@ref(fig:cons)e).

The prevention of biodiversity loss is a key goal of conservation ecologists,
and the concept of protection has long been a pillar of biodiversity
conservation [@watson2014]. Until roughly 2000, *park* was the most frequently
used term related to forms of geographic protection (Fig. \@ref(fig:cons)f).
*Protected areas* has grown steadily over the past eight decades with the growth
in *marine protected areas* showing a similar pattern, but lagging by several
decades (Fig. \@ref(fig:cons)f). These patterns of usage approximately mirror
the growth rate of protected land and sea area globally [@watson2014]. Many of
the key forms of geographic protection, including *parks*, *reserves*,
*protected areas*, and *preserves* predated the common usage of the term
*conservation* (Fig. \@ref(fig:cons)a,f), although this could be due in part to
several of these also acting as verbs. Nevertheless, the clear and sustained
rise in all terms related to geographic protection over eight decades points to
their continued importance in conservation and applied ecology.

## Social sciences and ecology

Over the last few decades, there has been increasing attention to human
dimensions in ecology and biodiversity conservation. Since the 1990s, there has
been an exponential increase in research on market or community-based
conservation interventions (Fig. \@ref(fig:social)a), particularly environmental
certification programs and payment for ecosystem services schemes such as the
Reducing Emissions from Deforestation and Forest Degradation (REDD) program. We
also observe an increased focus on human wellbeing (Fig. \@ref(fig:social)b),
with a spike of research on human health in the 1970s and more recently, an
overall growth in research on poverty, food security and overall human wellbeing
since the 1990--2000s. Given the increased focus on the human dimensions of
biodiversity conservation over the last decades [@bennett2017], it was expected
that social science methods such as interviews and questionnaires would become
more widely used in the literature (Fig. \@ref(fig:social)c). However, more
qualitative methods such as focus groups, ethnography or participant observation
remain scarcely used which supports the assertion that ecology and conservation
continue to rely mostly on quantitative methods (REF?). Parallel to the
increased focus on human wellbeing since the 1970s was the increased research on
various stakeholders and local communities (Fig. \@ref(fig:social)d). Yet, it is
clear that key stakeholder groups such as indigenous people are still greatly
underrepresented if we take into account how much land is under indigenous
management [@garnett2018].


<!--

Commented out discussion text:

Interventions

The 1992 Rio Summit played a key role in advancing ecosystem-based approaches to conservation, directly and indirectly spurning a plethora of conservation and research initiatives across the globe (Spalding et al 2013). For example, the Forest Stewardship Council was certification scheme initiated in 1993 in response to perceived inaction from the Rio Summit (FSC 2019,
 https://us.fsc.org/en-us/who-we-are/our-history). Since then certification schemes have expanded considerably,  with two environmental certification schemes (Rainforest Alliance, Marine Stewardship Council) alone account for 10%, 20%, and 14% of the world's cocoa, tea, and wild marine catch production (ref). Other resource management approaches such as ecotourism also took off in the 1980 and 90s, where it was included in the development strategy of almost every developing country by the 1990s [@moreno2005]. This exponential increase in coverage and use of these management strategies are likely drivers for the increased attention in the literature.

Human wellbeing
- Most of the research on human wellbeing in the corpus centers on poverty, likely advanced by the environmental discourse surrounding ecosystem services in the 2000s.The feedbacks between poverty and biodiversity are well discussed in the literature, where biodiversity conservation is seen as both a contributor and alleviator of poverty (Turner et al 2012). The Millenium Ecosystem Assessment (2005) however, advanced research and action around the concept of ecosystem services, where there was growing interest in how environmental improvement can promote (and not harm) various aspects of human wellbeing such as poverty alleviation. While the ecosystem service discourse has since been reframed (Diaz et al 2008), the causal links remain understudied (Suich et al 2005).


Methods

- Given the increased focus on the human dimensions of biodiversity conservation over the
  last decades [@bennett2017] it was expected that social science methods would become
  more widely used in the literature.
- While it may seem surprising to see interviews be more used than questionnaires, given
  that most ecologists and conservationists have a quantitative background, this could be
  a matter of terminology and questionnaires are a form of structured interview and are
  often referred to as such [@newing2010].
- More qualitative methods such as focus groups,
  ethnography or participant observation remain scarcely used which supports the assertion
  that ecology and conservation continue to rely mostly on quantitative methods

Stakeholder

- Increased use of stakeholder related focus suggests and increased focus on the social
  sciences across conservation and ecology. Yet, it is clear that key stakeholder groups
  such as indigenous people are still greatly underrepresented if we take into account ow
  much land is under indigenous management [@garnett2018]
- Yet, differences in scale of use between terms such as "stakeholder" or "local
  community" and those such as "participatory" suggest that most of the focus so far has
  been on characterizing stakeholders and their views and less on their direct involvement
  on processes related to conservation and management of wildlife.

David: References:
Spalding MD, Meliane I, Milam A, Fitzgerald C, Hale LZ. 2013. Protecting Marine Spaces: Global Targets and Changing Approaches. Ocean Yearb. 27, pp. 213–48
Díaz S, Pascual U, Stenseke M, Martín-López B, Watson RT, et al. 2018. Assessing nature’s contributions to people. Science (80-. ). 359(6373):270–72
Turner WR, Brandon K, Brooks TM, Gascon C, Gibbs HK, et al. 2012. Global Biodiversity Conservation and the Alleviation of Poverty. Bioscience. 62(January):85–92
Millennium Ecosystem Assessment. 2005. Ecosystems and Human Well-Being: Synthesis. Island Press, Washington D.C.
Suich H, Howe C, Mace G. 2015. Ecosystem services and poverty alleviation : A review of the empirical links. Ecosyst. Serv. 12:1–11

-->


# Discussion

# Acknowledgements

JSTOR, Smith,  Smith Fellows, M.P. Dombeck, S.G. Foster, anyone who helped and declines to be an
author...

# Methods

## Data

We worked with the JSTOR data team to extract n-gram data from the fulltext of their database for a set of journals relevant to ecology and conservation.

As a group, we reviewed all journals that were part of the JSTOR categories TODO
to evaluate their suitability for this analysis. We removed all journals that
were specific to taxa lower than kingdom (e.g., we retained "Plant Ecology" but
not "The Wilson Journal of Ornithology"). We removed all journals that were not
in English. We removed all journals that were not relevant to ecology or
conservation (e.g., we removed journals that were purely biology focused). We
removed journals that appeared in the JSTOR database for less than TODO years
unless they were still in the database as of 2010. We removed journals that were
too region specific. Specifically, be removed to journals that were longitude
specific but retained journals that were latitude specific (e.g., be retained
"Arctic and Alpine Research" but not "Great Basin Naturalist Memoirs"). In
total, our corpus included TODO journals (Table TODO).

We focused on 1-, 2-, and 3-grams since most common terms we were interested in were three words or less and the computational burden increased substantially at 4-grams.

Initial analyses revealed a number of data-cleaning steps that were necessary prior to our final analysis. Our initial corpus was dominated by data from Proceedings of the National Academy of Sciences (PNAS), which also publishes a high volume of papers not relevant to ecology or conservation. Therefore, we excluded all papers from PNAS that did not include one of the 1-grams TODO. We removed a series of TeX terms that were inadvertently included from the American Naturalist (Table TODO). We limited our analysis to 1930--2010. Before 1930, there was a considerably more limited set of journals included in the corpus and after 2010, the JSTOR corpus did not yet have data for all journals present in 2010 --- the number of journals present and the total number of words began to decline (Fig. TODO). These issues led to presumably spurious trends before 1930 or after 2010.

- how many papers in end, how many words
- List this in the supplement: Bad-amnat.txt: 28

- Standardized per total number of 1-grams each year
- List this in the supplement: Pnas_exluded_pub_ids.rds: 112259
- Supplementary figure of total account by journals over time
- Table of included journals
- Table of excluded journals and why (could combine with the included journals table)

## Top terms by decade

- Top terms by decade
- Start with top 5000 over entire time span
- Filter out grams with numbers
- Filter out grams with less than 3 characters
- For 1-grams: retain only nouns, koRpus::treetag() in English; from here on in work with lemmas
- Take top 500 for 1-grams overall
- For 2-grams: retain only adjective and nouns; from here on in work with lemmas
- Retain only those in which the first and second word have > three letters
- Exclude a number of 2-grams that are mostly affiliations or journal names:

(put this in the supplement as a table)
exclude <- c("american naturalist", "ecological monographs",
  "biol bull", "woods hole", "experi ments",
  "condi tions", "indi viduals", "comp physiol",
  "empty declaremathsizes", "university press",
  "conservation biology", "ecological society",
  "coastal research", "Journal compilation",
  "Blackwell publishing", "british ecological",
  "ecological applications", "cambridge university",
  "authors journal", "canadian journal",
  "royal society", "ecol evol", "state university",
  "springer verlag", "phil trans", "much more", "same time",
  "united states", "other hand", "philosophical transactions",
  "corresponding editor", "ecol monogr", "conserv biol",
  "ecol lett", "popu lations", "ecology letters",
  "research institute", "press chicago", "ecol syst",
  "funct ecol", "change biology", "author contributions",
  "phil wrans", "portugal issn", "nati acad", "proc nati",
  "corresponding author")

- Take top 500 for 2-grams
- Remove the following 1-grams

(put this in the supplement as a table)
pop1 <- pop1 %>% filter(!gram %in% c("fig", "use", "doi", "case"))
pop1 <- pop1 %>% filter(!gram %in% c("tion", "cent", "while", "results"))
pop1 <- pop1 %>% filter(!gram %in% c("table", "figure", "journal"))
pop1 <- pop1 %>% filter(!gram %in% c("university", "author", "eve"))

- Take top 9 1- and 2-grams from 1940–1950 and 2000–2010 for plotting
- For most rapid increases and decreases:
- Fit GLM for 1930–1960 and 1980–2010 total ~ year, offset = log(total_words), quasipoisson(link = “log) and record slope
- Take top n terms from 1940s and 2000s based on most positive and most negative slopes
- Curated panels

## Curated panels

- Talk about the benefits of ‘hand curation’ by a large group of ecologists working in their field
- Combined related terms that would refer to the same thing. E.g. ‘mixed effects model’ and ‘mixed-effects model’, ‘GLM’ and ‘generalized linear model’.
- Excluded terms that appeared frequently in journal names (would we picked up in headers and footers and in references)
- Use a categorical colour scheme to do note all hand-picked panels

# Figures

```{r decades, fig.cap = "**Top n-grams from the 1940s and 2000s.** (**a–d**) Top 9 1-gram nouns and 2-gram nouns or adjectives from the 1940s and 2000s. Labels refer to \"lemmas\" or root words. For example, plant and plants as n-grams are both combined and labelled as \"plant\". (**e–f**) Most rapidly increasing 1-gram nouns and 2-gram nouns or adjectives from 1980–2010. Light grey lines indicate frequency of the n-gram per 100,000 words. Dark coloured trend lines and associated shaded ribbons represent generalized additive model (GAM) fits and 95% confidence intervals (see Supporting Material)."}
include_graphics(here("figs/decades-and-booms-viridis.pdf"))
```

\clearpage

```{r blanks, fig.cap = "**Top fill-in-the-blank 2-gram phrases.** Each panel shows the top eight 2-gram terms where the *blank* in the panel label is filled in by the noun or adjective indicated beside each trend. For example, in panel **a**, \"Species *blank*\" with the term \"richness\" corresponds to \"species richness\". The top n-grams are defined based on summing the occurrences throughout the entire time period thereby weighting recent years more heavily."}
include_graphics(here("figs/blanks-viridis5.pdf"))
```

\clearpage

```{r ecology, fig.cap = "General ecology..."}
include_graphics(here("figs/ecology-panels3.pdf"))
```

\clearpage

```{r methods, fig.cap = "**Data analysis, statistical methods, and genetics.**"}
include_graphics(here("figs/methods-models-genetics2.pdf"))
```

\clearpage

```{r cons, fig.cap = "**Conservation and applied ecology.**"}
include_graphics(here("figs/conservation-human-impacts.pdf"))
```

\clearpage

```{r social, fig.cap = "**Social science and ecology.**"}
include_graphics(here("figs/social-science-panels3.pdf"))
```

\clearpage

\renewcommand{\thefigure}{S\arabic{figure}}
\renewcommand{\thetable}{S\arabic{table}}
\setcounter{figure}{0}
\setcounter{table}{0}

# Supporting Information

\clearpage

```{r declines-supp, fig.cap = "TODO"}
include_graphics(here("figs/booms-decline.pdf"))
```

\clearpage

```{r blanks-supp, fig.cap = "TODO"}
include_graphics(here("figs/blanks-extras-2018-08-09.pdf"))
```

\clearpage

```{r stats-supp, fig.cap = "TODO"}
include_graphics(here("figs/stats-supp.pdf"))
```

\clearpage

```{r genetics-supp, fig.cap = "TODO"}
include_graphics(here("figs/genetics-supp.pdf"))
```

\clearpage

# References
