---
title: "Trends in ecology and conservation over eight decades"
author:
- "Sean C. Anderson^1^"
- "Paul R. Elsen^2^"
- "Brent B. Hughes^3^"
- "Rebecca K. Tonietto^4^"
- "Add Your Name Here in Alphabetical Order^X^"
date: |
  ^1^Pacific Biological Station, Fisheries and Oceans Canada
     Nanaimo, BC, V6T 6N7, Canada; sean.anderson@dfo-mpo.gc.ca\
  ^2^Here\
  ^3^Here\
  ^4^Here\
  ^X^Add Your Address Here
output:
  bookdown::pdf_document2:
    number_sections: no
    toc: no
    template: "article.tex"
bibliography: "refs.bib"
csl: "nature.csl"
link-citations: yes
linkcolor: "blue"
urlcolor: "blue"
abstract: >
  The abstract will go here.
---

\clearpage

```{r, echo = FALSE, message = FALSE}
library(knitr)
library(here)
opts_chunk$set(echo = FALSE, message = FALSE, warnings = FALSE)
```

Introductory paragraph. Citation [@michel2011].

Paragraph that introduces the approach

# Broad trends in popularity

Fig. \@ref(fig:decades)
Fig. \@ref(fig:S-booms)
Fig. \@ref(fig:blanks)

- A: 'biodiversity conservation' first appears in the corpus in X (about 1990) and quickly became the most common word associated with conservation by nearly three-fold, perhaps at the expense of 'nature conservation', which peaked in the mid 1990s.

- B: Forest, terrestrial, and marine 'ecosystem' were all similarly common in the corpus as of 2010 with 'marine ecosystem' experiencing the most rapid increased since the 1990s. In the 1980s 'forest ecosystem' was by far the most common 2-gram ecosystem term.

- C: since the 1950s, 'natural' was the most popular term associated with 'population'
- as of 2010, 'human population' surpassed 'natural population'

- D: species is the most common term associated with 'diversity' and has been since any of the common 'diversity' terms started to be included in the corpus as of the 1950s
- 'genetic diversity' has rocketed from being a rarely discussed form of diversity until about 1990 to being the second most common diversity phrase as of X (around 2000). As of 2010 its use was still rapidly increasing. 
- 'species diversity' saw a decline in use between ~1975 and 1990 followed up by an increase in use until X (about 2005).
- blank diversity terms as a group are discussed more than any of the other blank terms here (largest y axis values by 2 fold).

- E: although genetic diversity was not frequently talked about until the 1990s (D), 'genetic variability' was talked about more than 'genetic diversity' until about 1990 (check), and now 'genetic diversity' is included about 8 times more often than 'genetic variability'
- 'temporal variability' was the most frequently discussed type of variability as of 2010, closely followed by spatial variability 
- 'climate variability' didn't appear in the corpus until 1988 (check), but quickly became one of the top 3 types of variability discussed in the literature (TODO: perhaps combined climate and climatic, which would put climate approximately the same point as temporal)

- F: 'species distribution' the most common form of distribution included, but didn't see rapid growth until after 1990
- statistical distributions mixed in: normal, frequency, probability 
- from 1930 to ~1950 'vertical distribution' was the most common term; this peaked around 1940 and has consistently declined since around 1970 (TODO: WHY WAS THIS BIG?)

# Ecology and scale

Fig. \@ref(fig:ecology)

# Ways of analyzing ecology

Fig. \@ref(fig:methods)

## A: Models for inference

- 'Regression' saw continued and rapid growth from 1930s to late 2000s approaching 'correlation' [thought: it's possible we should remove correlation since it used a lot in contexts beyond models for inference]
- References to 'ANOVA' started in substantial quantity in the mid 1970s and peaked around 2000 seeing a rapid decline from 2000-2010
- References to generalized linear models (GLMs) have steadily increased and surpassed the frequency of 't-test' as of 2007(?), which has been declining in use since around 2000

## B: Modelling paradigms

- Although 'least-squares' has been steadily increasing in use since the beginning of the corpus in 1930, it was rapidly surpassed by Bayesian, maximum likelihood, and information theoretic terms in ~2000
- 'maximum likelihood' used to be used more frequently than 'Bayesian', but as of ~2000, 'Bayesian' terms surpassed 'maximum likelihood'
- As of 2010, 'Bayesian' terms were used approximately twice as often as the phrase 'maximum likelihood'
- The Bayesian Markov chain Monte Carlo sampling approach 'MCMC' first appears in 1992(?) and saw a rapid increase through to the end of the corpus in 2010

## C: Statistical significance 

- (TODO: did we include 'statistical significance' itself?)
- Some sentence about endless debates on statistical significance in the ecology literature
- Use of the phrase 'null hypothesis' peaked in the 1980s and the phrase 'significant difference' peaked in use around 1990 and has declined since 
- 'p-value' and 'confidence interval' appeared in equal frequency as of 2010, although both are often referred to by abbreviations that would be missed in our corpus (e.g. 'p = ' or 'CI').
- 'power analysis' remains a rarely used phrase despite numerous pleas by ecological statisticians (REF)

## D: Supporting information

- 'supplementary material', 'supporting information', and 'SOM' (collectively shown as 'supplementary material') have seen a meteoric rise since around 2000, likely coinciding with the rise of the Internet and online journal publishing
- this rise has coincided with a decline in the term 'unpublished data'

## E: Genetics 1

## F: Genetics 2

Fig. \@ref(fig:stats-supp)
Fig. \@ref(fig:genetics-supp)

# Conservation and ecology

Fig. \@ref(fig:conservation)

# Social science and ecology

Fig. \@ref(fig:social)

# Some concluding subheading

# Acknowledgments

# Methods

## Data source and filtering

- JSTOR
- Picking journals --- rules, table of all plus chosen and why
- what data looks like
- PNAS filtering
- 

## Assessing popularity

## Trend model fitting

\clearpage

```{r decades, fig.cap = "(A--D) Top 9 1-gram nouns and 2-gram nouns/adjectives from the 1940s and 2000s. Labels refer to 'lemmas' or root words. For example, plant and plants as n-grams are both combined and labelled as 'plant'. (E, F) Most rapidly increasing 1-gram nouns and 2-gram nouns/adjectives from 1980--2010."}
include_graphics(here("figs/decades-and-booms-viridis.pdf"))
```

\clearpage

```{r blanks, fig.cap = "Top 8 terms followed by the term in the top left corner where the terms are either nouns or adjectives. The top n-grams are defined based on summing the occurrences throughout the entire time period thereby weighting recent years more heavily."}
include_graphics(here("figs/blanks-viridis2.pdf"))
```

\clearpage

```{r ecology, fig.cap = "General ecology... TO BE FIXED"}
include_graphics(here("figs/ecology-panels.pdf"))
```

\clearpage

```{r methods, fig.cap = "Methods and genetics..."}
include_graphics(here("figs/methods-models-genetics2.pdf"))
```

\clearpage

```{r conservation, fig.cap = "Conservation..."}
include_graphics(here("figs/conservation-human-impacts.pdf"))
```

\clearpage

```{r social, fig.cap = "Social science and ecology..."}
include_graphics(here("figs/social-science-panels3.pdf"))
```

\clearpage

\renewcommand{\thefigure}{S\arabic{figure}}
\renewcommand{\thetable}{S\arabic{table}}
\setcounter{figure}{0}
\setcounter{table}{0}

# Supporting Information

\clearpage

```{r S-booms, fig.cap = "TODO"}
include_graphics(here("figs/booms.pdf"))
```

\clearpage

```{r stats-supp, fig.cap = "TODO"}
include_graphics(here("figs/stats-supp.pdf"))
```

\clearpage

```{r ecology-supp, fig.cap = "General ecology... TO BE FIXED"}
include_graphics(here("figs/ecology_supp_panels_06_19.pdf"))
```

\clearpage

```{r genetics-supp, fig.cap = "TODO"}
include_graphics(here("figs/genetics-supp.pdf"))
```

\clearpage

# References
