---
title: "Trends in ecology and conservation over eight decades"
author:
- "Sean C. Anderson^1^"
- "Paul R. Elsen^2^"
- "Brent B. Hughes^3^"
- "Rebecca K. Tonietto^4^"
- "Add Your Name Here in Alphabetical Order^X^"
date: |
  ^1^Pacific Biological Station, Fisheries and Oceans Canada
     Nanaimo, BC, V6T 6N7, Canada; sean.anderson@dfo-mpo.gc.ca\
  ^2^Here\
  ^3^Here\
  ^4^Here\
  ^X^Add Your Address Here
output:
  bookdown::pdf_document2:
    number_sections: no
    toc: no
    template: "article.tex"
bibliography: "refs.bib"
csl: "nature.csl"
link-citations: yes
linkcolor: "blue"
urlcolor: "blue"
abstract: >
  The abstract will go here.
---

\clearpage

```{r, echo = FALSE, message = FALSE}
library(knitr)
library(here)
opts_chunk$set(echo = FALSE, message = FALSE, warnings = FALSE)
```

The field of ecology has experienced rapid growth since the discipline specific journal,
Ecology, was first published over a century ago [@reiners2017; @kim2018]. Today, there are
approximately XX ecological journals, representing many subdisciplines within the field,
spanning in scope from general to applied to theoretical. In light of the rapid
diversification of the field, accomplishing a broad can be difficult...

In an effort to reduce human biases, the field of culturomics has increasingly been
employed in the evaluation of past and present trends in literature [@michel2011;
@ladle2016]. Through quantification of word use in relevant corpa, such as the large
bodies of text accessible in online journal databases, one can glean a better
understanding of trends. Specifically, word use in the published literature can serve as
a proxy for tracking realized (versus perceived) importance (sensu WHO WROTE THAT ONE),
though rankings of perceived importance are also valuable insights (e.g., Reiners et al.,
2017). This method has been applied to subsets of the ecological literature, notably
a century of titles and abstracts in the Ecological Society of America journal, Ecology
[@kim2018], automated content analysis of titles and abstracts in top ecology journals
based on impact factor [@mccallen2019], and more specific research questions restricted to
certain regions and/or taxa (e.g., Beale, 2018).

Here, we build on previous analyses [@carmel2013; @reiners2017; @kim2018; @mccallen2019]
by providing the first full-text analysis of ecology and conservation journals over eight
decades encompassing 52 journals, 131,533 papers, and over half a billion words. We base
our analysis on the JSTOR full-text corpus of "n-grams" from 1930 to 2010 for all journals
that regularly publish ecological or conservation papers and are not regionally or
taxonomically exclusive (see Methods). An n-gram is a sequence of terms separated by
a space. For example, "biogeography" is a 1-gram and "body size" is a 2-gram. We
standardized n-gram frequency by total words per year and analysed trends over time for
a selection of n-grams. We derived our n-gram selection through both algorithmic and
hand-curated approaches: (1) drawing on the most frequent and rapidly growing/declining
n-grams in various decades and (2) developing logical groupings of terms that fall under
key ecology and conservation themes (see Methods).

# Results

## Broad trends in popularity

A mission driven discipline: [@meine2006]

(Fig. \@ref(fig:decades)) (biggest then and now; biggest climbers (and biggest losers in Supp.)

We used a fill-in-the-blank strategy to algorithmically examine the dominant 2-grams
associated with levels of scale in ecology (Fig. \@ref(fig:blanks)). *Species richness*
and *plant species* have been the dominant adjective and noun uses of the term species,
respectively (Fig. \@ref(fig:blanks)ab). Notably, *native* came from behind around 2000 to
become the third most common term proceeding *species* as of 2010 (Fig.
\@ref(fig:blanks)b). As an adjective, the term *population* has been primarily associated
with *size*, *growth*, *dynamics*, and *density*, with *population growth* following
approximately exponential growth itself (Fig. \@ref(fig:blanks)d). Conversely, *natural*
*population* was the dominant noun-form of *population*, but was surpassed by *human
population* as of 2010 (Fig. \@ref(fig:blanks)e). Ecologists have written about *community
structure*, and *community composition* more than any other adjective-form of *community*
and about *plant communities*, within our corpus, over three times(?) more than any other
form of community (Fig. @ref(fig:blanks)gh). Ecologists first used the term *ecosystem* as
a noun long before using it as an adjective starting around 1990 (Fig.
\@ref(fig:blanks)jk). As a noun, *ecosystem* has been most commonly associated with
*forest*, *terrestrial*, and *marine*, with the latter seeing a sharp uptick since 2000
(Fig. \@ref(fig:blanks)k). As an adjective, *ecosystem service* and *ecosystem function*
are by far the dominant 2-grams (Fig. \@ref(fig:blanks)j).

Using the same approach we also examined adjectives associated with conservation,
diversity, experiment, and analysis (Fig. \@ref(fig:blanks)). *Biodiversity conservation*
did not appear until 1990(?) in our corpus but is now used over twice as often as the next
most common, *nature conservation* (Fig. \@ref(fig:blanks)c). *Genetic diversity* has
skyrocketed since the early 1990s to become the dominant adjective associated with
diversity (Fig. \@ref(fig:blanks)f). *Field* and *laboratory experiment* peaked around
1990 and have been declining since (Fig. @ref(fig:blanks)i). *Statistical*, the first
adjective associated with *analysis* that made the top eight terms, continued to see
growth as of 2010 (Fig. \@ref(fig:blanks)l); however, *data analysis*, which didn't appear
until 1950, surpassed statistical analysis around 2000 (Fig. @ref(fig:blanks)l).
*Meta-analysis*, which first appeared in 1988(?) in our corpus, has seen rapid growth to
become the most common adjective associated with analysis as of 2010 (Fig.
@ref(fig:blanks)l).

## Community ecology

Fig. \@ref(fig:ecology)

## Statistics and data analysis

Ecology has increasingly become a data- and model-centric discipline in recent decades
(Fig. @ref(fig:decades)). *Regression*, an overarching term encompassing many statistical
approaches, saw continued and rapid growth in use since the 1950s, approaching
*correlation* by 2005 (Fig. @ref(fig:methods)a). References to *ANOVA* and *t-tests* both
peaked around 2000, while mentions of generalized linear models (*GLMs*) steadily
increased in frequency surpassing *t-tests* around 2007(?) (Fig. \@ref(fig:methods)a). In
terms of how such models were fit, *least-squares*, formerly the dominant paradigm, was
rapidly surpassed by *Bayesian*, *maximum likelihood*, and *information theoretic* terms
around 2000; as of 2010, the term *Bayesian* was used over twice as often as *maximum
likelihood* (Fig. \@ref(fig:methods)b). The Markov chain Monte Carlo sampling method
(*MCMC*), which combined with modern computing power has been responsible for the boom in
applied Bayesian data analysis [@gelman2014b] first appears in the corpus in 1994
[@thompson1994], 24 years after [@hastings1970] described the concept. Such statistical
approaches and paradigms have been associated with endless debates about the role of
hypothesis testing in ecology (REFs). Regarding hypothesis testing, use of the phrase
*null hypothesis* peaked in the 1980s and the phrase *significant difference* peaked
around 1990 and has declined since (Fig. \@ref(fig:methods)c). The associated terms
*p-value* and *confidence interval* appeared in approximately equal frequency as of 2010
(Fig. \@ref(fig:methods)c), although both are often referred to by abbreviations missed in
our corpus (e.g. 'p =' or 'CI'). *Power analysis* remains a rarely used term despite
numerous pleas of its importance [@nakagawa2007; @smith2011d]. The increased frequency of
so many data- and model-centric terms, along with the advent of online publishing, has
coincided with the meteoric rise of *supplementary material* n-grams since around 2000 ---
the 2-gram itself had the second most rapid increase across all 2-grams from 2000--2010
(Fig. \@ref(fig:decades)f) --- and a decline in *unpublished data* (Fig.
\@ref(fig:methods)d).

## Genetics

## Conservation and applied ecology

*Conservation* and themes related to applied ecology represented some of the fastest
growing themes in modern ecology (Fig. \@ref(fig:decades)e). Conservation as a field
originated alongside the formation of the Society for Conservation Biology in 1985
[@meine2006], prior to which the roughly synonymous term *preservation* was used as
frequently in ecological literature (Fig. @ref(fig:cons)a). *Biodiversity*, a core concept
of conservation, replaced the terminology *biological diversity* that had been in use
since the 1960s. Alongside *conservation*, *biodiversity* is one of the most rapidly
growing terms we analyzed in the corpus (Fig. 1e). Given the prominent focus on
biodiversity conservation in the field of ecology, ecologists have increasingly studied
the major threats to biodiversity loss: *habitat loss*, *invasive species*, *pollution*,
*overpopulation*, *overexploitation*, and *climate change* (Fig. \@ref(fig:cons)b).
Despite *overexploitation* being considered the most prevalent threat of species
extinctions worldwide [@maxwell2016], the concept has received the least attention from
ecologists both historically and currently (Fig. \@ref(fig:cons)b). Up until the early
1990s, *pollution* was the leading concept in the context of threats to biodiversity ---
its use in the ecological literature having peaked in the mid 1970s (Fig.
\@ref(fig:cons)b). Interestingly, frequencies of the concept *ozone*, typically associated
with studies of pollution, showed similar responses as *pollution*, but with a lag of
approximately 15 years (Fig. \@ref(fig:cons)c). *Pollution* was then surpassed by *climate
change* and subsequently by *invasive species*, two threats that now vastly outweigh all
other threats in terms of their frequency of usage (Fig. \@ref(fig:cons)b) and two of the
top three fastest growing terms in all of ecology (Fig. 1f).

A multitude of concepts originated alongside the proliferation of studies of climate
change, habitat loss, and overexploitation (Fig. \@ref(fig:cons)c-e). With such relatively
recent concept formations, most of these concepts are experiencing continued growth. For
example, concepts related to climate change, such as *ocean acidification*, *range
shifts*, and *climate extremes* have shown sharp upticks since the mid 2000s (Fig.
\@ref(fig:cons)c). Other concepts have shown more complex patterns. For example,
*sea-level rise* showed a large spike in usage in the mid 1990s, a dramatic downturn in
usage by 2000, and then another sharp increase thereafter (Fig. \@ref(fig:cons)c).
*Fragmentation* rose sharply following the common usage of *habitat loss* around 1990, but
its use has been in decline since about 2000 (Fig. \@ref(fig:cons)d). In terms of modes of
overexploitation, which include both methods of species exploitation and resource
extraction, *fishing* is currently the leading concept, followed by *hunting* and
*logging* (Fig. \@ref(fig:cons)e). Historically, *hunting* and *fishing* have exchanged
positions of dominance in the ecological literature roughly every decade, showing
predator-prey-like dynamics in their frequency distributions over time (Fig.
@ref(fig:cons)e). Modes of exploitation of non-animal resources, such as *logging*,
*harvesting*, and *mining* have consistently been discussed less in the ecological
literature compared to modes of animal exploitation (Fig. \@ref(fig:cons)e).

The prevention of biodiversity loss is a key goal of conservation ecologists, and the
concept of protection has long been a pillar of biodiversity conservation [@watson2014].
Until roughly 2000, *park* was the most frequently used term related to forms of
geographic protection (Fig. @ref(fig:cons)f). *Protected areas* has grown steadily over
the past eight decades with the growth in *marine protected areas* showing a similar
pattern, but lagging by several decades (Fig. @ref(fig:cons)f). These patterns of usage
approximately mirror the growth rate of protected land and sea area globally
[@watson2014]. Many of the key forms of geographic protection, including *parks*,
*reserves*, *protected areas*, and *preserves* predated the common usage of the term
*conservation* (Fig. \@ref(fig:cons)a,f), although this could be due in part to several of
these also acting as verbs. Nevertheless, the clear and sustained rise in all terms
related to geographic protection over eight decades points to their continued importance
in conservation and applied ecology.

## Social sciences and ecology

# Discussion

# Acknowledgements

JSTOR, Smith,  Smith Fellows, M.P. Dombeck, S.G. Foster, anyone who helped and declines to be an
author...

# Methods

## Data

- JSTOR, ngram approach, 1-, 2-, and 3-grams
- how selected initial categories, how many journals
- How filtered down journals (not taxon specific, …), how many journals left
- how many papers in end, how many words
- Date range and why
- Standardized per total number of 1-grams each year
- Bad-amnat.txt: 28
- Pnas_exluded_pub_ids.rds: 112259
- Why limited it to 1930–2010
- Table of journals included
- Supplementary figure of total account by journals over time

## Top terms by decade

- Top terms by decade
- Start with top 5000 over entire time span
- Filter out grams with numbers
- Filter out grams with less than 3 characters
- For 1-grams: retain only nouns, koRpus::treetag() in English; from here on in work with lemmas
- Take top 500 for 1-grams overall
- For 2-grams: retain only adjective and nouns; from here on in work with lemmas
- Retain only those in which the first and second word have > three letters
- Exclude a number of 2-grams that are mostly affiliations or journal names:

(put this in the supplement as a table)
exclude <- c("american naturalist", "ecological monographs",
  "biol bull", "woods hole", "experi ments",
  "condi tions", "indi viduals", "comp physiol",
  "empty declaremathsizes", "university press",
  "conservation biology", "ecological society",
  "coastal research", "Journal compilation",
  "Blackwell publishing", "british ecological",
  "ecological applications", "cambridge university",
  "authors journal", "canadian journal",
  "royal society", "ecol evol", "state university",
  "springer verlag", "phil trans", "much more", "same time",
  "united states", "other hand", "philosophical transactions",
  "corresponding editor", "ecol monogr", "conserv biol",
  "ecol lett", "popu lations", "ecology letters",
  "research institute", "press chicago", "ecol syst",
  "funct ecol", "change biology", "author contributions",
  "phil wrans", "portugal issn", "nati acad", "proc nati",
  "corresponding author")

- Take top 500 for 2-grams
- Remove the following 1-grams

(put this in the supplement as a table)
pop1 <- pop1 %>% filter(!gram %in% c("fig", "use", "doi", "case"))
pop1 <- pop1 %>% filter(!gram %in% c("tion", "cent", "while", "results"))
pop1 <- pop1 %>% filter(!gram %in% c("table", "figure", "journal"))
pop1 <- pop1 %>% filter(!gram %in% c("university", "author", "eve"))

- Take top 9 1- and 2-grams from 1940–1950 and 2000–2010 for plotting
- For most rapid increases and decreases:
- Fit GLM for 1930–1960 and 1980–2010 total ~ year, offset = log(total_words), quasipoisson(link = “log) and record slope
- Take top n terms from 1940s and 2000s based on most positive and most negative slopes
- Curated panels

## Curated panels

- Talk about the benefits of ‘hand curation’ by a large group of ecologists working in their field
- Combined related terms that would refer to the same thing. E.g. ‘mixed effects model’ and ‘mixed-effects model’, ‘GLM’ and ‘generalized linear model’.
- Excluded terms that appeared frequently in journal names (would we picked up in headers and footers and in references)
- Use a categorical colour scheme to do note all hand-picked panels

# Figures

```{r decades, fig.cap = "Overall"}
include_graphics(here("figs/decades-and-booms-viridis.pdf"))
```

\clearpage

```{r blanks, fig.cap = "Blanks"}
include_graphics(here("figs/blanks-viridis5.pdf"))
```

\clearpage

```{r ecology, fig.cap = "Community ecology..."}
include_graphics(here("figs/ecology-panels3.pdf"))
```

\clearpage

```{r methods, fig.cap = "Methods and genetics..."}
include_graphics(here("figs/methods-models-genetics2.pdf"))
```

\clearpage

```{r cons, fig.cap = "Conservation..."}
include_graphics(here("figs/conservation-human-impacts.pdf"))
```

\clearpage

```{r social, fig.cap = "Social science and ecology..."}
include_graphics(here("figs/social-science-panels3.pdf"))
```

\clearpage

\renewcommand{\thefigure}{S\arabic{figure}}
\renewcommand{\thetable}{S\arabic{table}}
\setcounter{figure}{0}
\setcounter{table}{0}

<!--
# Supporting Information

\clearpage

```{r S-booms, fig.cap = "TODO"}
include_graphics(here("figs/booms.pdf"))
```

\clearpage

```{r stats-supp, fig.cap = "TODO"}
include_graphics(here("figs/stats-supp.pdf"))
```

\clearpage

```{r ecology-supp, fig.cap = "General ecology... TO BE FIXED"}
include_graphics(here("figs/ecology_supp_panels_06_19.pdf"))
```

\clearpage

```{r genetics-supp, fig.cap = "TODO"}
include_graphics(here("figs/genetics-supp.pdf"))
```

-->

\clearpage

# References
