---
title: "Trends in ecology and conservation"
author:
- Sean C. Anderson^1^
- Paul R. Elsen^2^
- Brent B. Hughes^3^
- Rebecca K. Tonietto^4^
- Add Your Name Here in Alphabetical Order^X^
date: |
  ^1^Pacific Biological Station, Fisheries and Oceans Canada 
     Nanaimo, BC, V6T 6N7, Canada; sean.anderson@dfo-mpo.gc.ca\
  ^2^here\
  ^3^here\
  ^4^here\
  ^X^Add Your Address Here
output: 
  bookdown::pdf_document2:
    keep_tex: no
    number_sections: no
    toc: no
    template: default.tex
bibliography: refs.bib
csl: nature.csl
link-citations: yes
linkcolor: blue
urlcolor: blue
abstract: >
  The abstract will go here.
---

\clearpage

```{r, echo = FALSE, message = FALSE}
library(knitr)
library(here)
opts_chunk$set(echo = FALSE, message = FALSE, warnings = FALSE)
```

Fig. \@ref(fig:decades)

Fig. \@ref(fig:S-booms)

Fig. \@ref(fig:blanks)

Fig. \@ref(fig:ecology)

Fig. \@ref(fig:methods)

Fig. \@ref(fig:conservation)

Fig. \@ref(fig:social)


Citation [@michel2011].

\clearpage

```{r decades, fig.cap = "(A--D) Top 9 1-gram nouns and 2-gram nouns/adjectives from the 1940s and 2000s. Labels refer to 'lemmas' or root words. For example, plant and plants as n-grams are both combined and labelled as 'plant'. (E, F) Most rapidly increasing 1-gram nouns and 2-gram nouns/adjectives from 1980--2010."}
include_graphics(here("figs/decades-and-booms-viridis.pdf"))
```

\clearpage

```{r blanks, fig.cap = "Top 8 terms followed by the term in the top left corner where the terms are either nouns or adjectives. The top n-grams are defined based on summing the occurrences throughout the entire time period thereby weighting recent years more heavily."}
include_graphics(here("figs/blanks-viridis2.pdf"))
```

\clearpage

```{r ecology, fig.cap = "General ecology... TO BE FIXED"}
include_graphics(here("figs/scale-panels-2.pdf"))
```

\clearpage

```{r methods, fig.cap = "Methods..."}
include_graphics(here("figs/methods-models-genetics.pdf"))
```

\clearpage

```{r conservation, fig.cap = "Methods..."}
include_graphics(here("figs/conservation-human-impacts.pdf"))
```

\clearpage

```{r social, fig.cap = "Social science and ecology..."}
include_graphics(here("figs/social-science-panels2.pdf"))
```

\clearpage

\renewcommand{\thefigure}{S\arabic{figure}}
\renewcommand{\thetable}{S\arabic{table}}
\setcounter{figure}{0}
\setcounter{table}{0}

# Supporting Information

\clearpage

```{r S-booms, fig.cap = "test"}
include_graphics(here("figs/booms.pdf"))
```

\clearpage

# References
